\clearpage
\pagenumbering{roman} 				
\setcounter{page}{1}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\chaptermark}[1]{\markboth{\chaptername\ \thechapter.\ #1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
\renewcommand{\headrulewidth}{0.1ex}
\renewcommand{\footrulewidth}{0.1ex}
\fancyfoot[LE,RO]{\thepage}
\fancypagestyle{plain}{\fancyhf{}\fancyfoot[LE,RO]{\thepage}\renewcommand{\headrulewidth}{0ex}}

\section*{\Huge Abstract}
\addcontentsline{toc}{chapter}{Abstract}	
$\\[0.5cm]$

\noindent A primary concern of the construction industry in Norway is the significant decline in labor productivity compared to other on-land industries. Statistics show a relative difference in labor productivity, compared to the ICT industry from the year 2000 up to 2016, of 106.4\%. The research in this project shows a strong correlation in how the construction industry is today and how the software industry was thirty years ago. Both industries are now utilizing agile management, and software supporting these methods. This case study looks at the new life science building project, of the University of Oslo, for the purpose of exploring the fundamental reasons for the gap in labor productivity between the ICT industry and the construction industry. The study is not to do a comparative analysis of labor productivity between the two, but to explore the phenomenon causing the gap.

Using semi-structured interviews and observations, with participants from the project management organization, analysis of the interviews identified three key findings: (1) problems in interaction between personnel, (2) problems in the decision making, and (3) problems in ignorance. Furthermore, the result shows two fundamental reasons causing these problems, that is, the actors' limited understanding of the new methods and actors' traditional view of contracts, interaction, and transparency. Based on these observations, the project proposes a more extensive use of a new digital tool, Cogito, to further explore the phenomenon causing the gap in labor productivity, in a lean construction project using digital tools.

\clearpage